Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-30 latex/article.tex
Working on 5 and 6.

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \vspace{-0.35cm}
  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
  \emph{Second row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
  \vspace{-0.35cm}
\end{figure}

@@

We first evaluate the curvature estimation on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top shows results of curvature tensor
estimation (mean, Gaussian, first and
second principal directions) on an OctaFlower at level $l_0$ (considered as our ground truth in the following).
Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
dynamic object. For this case, we simply evaluate the implicit expression at
each vertex of a cell to decide if such cell is included or not into
$\Ball{R}{\vx}\cap \Shape$ instead of updating the \emph{mipmap texture} of
densities at each time step. For all illustrations, we use directly normal
vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}.

Then, we compare the approximation made by computing curvature from level $l \ge
l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
seems to quickly converge to the ground truth results.
Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (maximal absolute difference for all vertices )
and $L_2$ error (mean absolute error of all vertices), as well the number of \emph{mipmap texture}
fetches. We can also see that the number of texel fetch, required to compute the
curvature, reduces drastically when computing approximations. However, at higher levels,
approximation errors become more important. Those levels
are thus never used in practice, they are presented here to illustrate how the
refining process converges to the $l_0$ level.
%We see that levels close to $l_0$
%lead very few error% than $l_0$,
%and should be considered for exploring our datasets
%in real-time, changing parameters on-the-fly and visualizing dynamic datasets.

We also compare them with the hierarchical algorithm (as discussed in
Section~\ref{sec:hierarchical}). This method introduces a higher error when compared with
$l_0$. This is due to the precomputation of the subdivision that no longer
ensures to fetch data at the center of a mipmap cell.
The GPU interpolation reduces the bias, but it doesn't remove it.

@@

When dealing with large datasets, we can not expect real-time curvature tensor
estimation if we consider the full resolution geometry, due the the huge amount of data process. By computing a
dynamically refined approximate curvature tensor estimation joined with an
adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
manage to maintain a real-time framerate by giving control over the amount of
data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
(in logarithmic scale) for a triangulation that is dynamically refined according
to its distance to the camera. We measured those timings using the multiresolution regular and
the hierarchical algorithm.

@@

We can first note that the required time for an object to compute the ground truth
curvature is usually as high as the time required to extract the geometry and to
compute all of the above levels. Using approximations is thus mandatory.
Another advantage with approximations, is that it allows us to get a visualisation of our object as soon as we run
the application. This allows for real-time interactions with the object, required in order to change
the visualized value, curvature radius, \ldots

>>>>

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
%    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
%    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \vspace{-0.35cm}
  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on ``OctaFlower'' with a digital domain of $130^3$.
  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
  \emph{Second row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
  \vspace{-0.35cm}
\end{figure}

@@

We first evaluate curvature estimations on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top shows results of curvature tensor estimation
(mean, Gaussian, first and second principal directions) on
``OctaFlower'' at level $l_0$ (considered as our ground truth in the
following).  Figure~\ref{fig:full}-bottom shows mean curvature
estimation in real-time on a dynamic object. For this case, we simply
evaluate the implicit expression at each vertex of a cell to decide if
such cell is included or not into $\Ball{R}{\vx}\cap \Shape$ instead
of updating the \emph{mipmap texture} of densities at each time
step. For all illustrations, we use directly normal vectors computed
by algorithm discussed in Section~\ref{sec:curv-tens-estim}.

Then, we compare the approximations made by computing curvature from
level $l \ge l_0$ in Figure~\ref{fig:refine}. We can see that results
using approximation seems to quickly converge to ground truth results.
Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$
error (maximal absolute difference for all vertices) and $L_2$ error
(mean \Jaco{squared errors} of all vertices), as well the number of
\emph{mipmap texture} fetches. We can also see that the number of
texel fetch, required to compute the curvature, reduces drastically
when computing approximations. However, at higher levels,
approximation errors become more important. Those levels are thus
never used in practice, they are presented here to illustrate how the
refining process converges to the $l_0$ level.
%We see that levels close to $l_0$
%lead very few error% than $l_0$,
%and should be considered for exploring our datasets
%in real-time, changing parameters on-the-fly and visualizing dynamic datasets.

We also compare them with the hierarchical algorithm (as discussed in
Section~\ref{sec:hierarchical}). This method introduces a higher error when compared with
$l_0$. This is due to the precomputation of the subdivision that no longer
ensures to fetch data at the center of a mipmap cell.
The GPU interpolation reduces the bias, but it does \Jaco{not} remove it.

@@

When dealing with large datasets, we \Jaco{cannot} expect real-time curvature tensor
estimation if we consider the full resolution geometry, due the the huge amount of data \Jaco{to} process. By computing a
dynamically refined approximate curvature tensor estimation joined with an
adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
manage to maintain a real-time framerate by giving control over the amount of
data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
(in logarithmic scale) for a triangulation that is dynamically refined according
to its distance to the camera. We measured those timings using the multiresolution regular and
the hierarchical algorithm.

@@

\Jaco{First} we can note that the required time to
compute the ground truth curvature \Jaco{for an object} is usually as high as the time
required to extract its geometry and to compute all of the above
levels. Using approximations is thus mandatory.  Another advantage
with approximations is that it allows us to get a visualisation of
our object as soon as we run the application. This allows for
real-time interactions with the object, required in order to change
the visualized \Jaco{quantity}, curvature radius, etc.
